A Taxonomy of Twists of Supersymmetric Yang--Mills Theories

### 2020-01-26 paper.tex
4d N=4 (2, 2)

Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$. Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. Moreover, fix a complex volume form on $L$. Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$. Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in S_+
\label{eq:8dHodgefamily}
\end{equation}
for $t\in\CC$. We have
\[(Q_t, Q_t) = t,\]
so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.

@@

Next, we check that the equivalence respects  the gradings. Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$. The rest of the fields organize into the following collections:
\begin{align*}
c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg) \\
a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2-4n] \\
\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[4n-1] \\
\phi + \psi + \varphi^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
\varphi + \psi^* + \phi^* &\in\Omega^{2, \bullet}(M; U\otimes K_M^{-1/2})[1-2n]
\end{align*}

@@

Note, however, that the twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above. In particular, this equivalence is not $\U(2)$-equivariant. In the present case the fields organize in the following collections:
\begin{align*}
c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
\phi + \psi + \varphi^*&\in\Omega^{1, \bullet}(M; \fg) \\
\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[-1] \\
\\
a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2] \\
\varphi + \psi^* + \phi^* &\in\Omega^{1, \bullet}(M; \fg)[1] \\
B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg)
\end{align*}
These are exactly the fields in $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg)$.
\end{proof}

@@

\begin{theorem}
\chris{Special rank $(2,2)$ deforming to generic rank $(2,2)$, by dimensional reduction from 5d $2_A$ deforming to $2_B$} $\mr{Map}(\RR^4_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

% \vspace{-10pt}
% \paragraph{Supersymmetry action:} 
% \begin{prop}
% Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
% \begin{align*}
% I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
% &\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
% &\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
% \end{align*}
% and
% \begin{align*}
% I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
% &\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
% &\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
% \end{align*}
% where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
% \end{prop}

>>>>

Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$. Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. Moreover, fix a complex volume form on $L$. Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
\[S_+\cong \CC Q_0\oplus \wedge^2 L\oplus \CC \Bar{Q}_0.\]
The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$. Consider a family of square-zero supercharges
\begin{equation}
Q_t = Q_0 + t\Bar{Q}_0\in S_+
\label{eq:8dHodgefamily}
\end{equation}
for $t\in\CC$. We have
\[(Q_t, Q_t) = t,\]
so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.

@@

Next, we check that the equivalence respects  the gradings. Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$. The rest of the fields organize into the following collections:
\begin{align*}
c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg) \\
\\
a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2-4n] \\
\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[4n-1] \\
\\
\phi + \psi + \varphi^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
\varphi + \psi^* + \phi^* &\in\Omega^{2, \bullet}(M; U\otimes K_M^{-1/2})[1-2n]
\end{align*}

@@

Note, however, that the twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above. In particular, this equivalence is not $\U(2)$-equivariant. In the present case the fields organize into the following collections:
\begin{align*}
c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
\phi + \psi + \varphi^*&\in\Omega^{1, \bullet}(M; \fg) \\
\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[-1] \\
\\
a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2] \\
\varphi + \psi^* + \phi^* &\in\Omega^{1, \bullet}(M; \fg)[1] \\
B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg)
\end{align*}
These are exactly the fields in $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg)$.
\end{proof}

@@

Consider a rank $(2, 2)$ supercharge $Q\in S_+\otimes W\oplus S_-\otimes W^*$. It defines embeddings $S_+^*\hookrightarrow W$ and $S_-^*\hookrightarrow W^*$ and the square-zero condition is that their images pair to zero. In other words, we have a short exact sequence
\[0\longrightarrow S_+^*\longrightarrow W\longrightarrow S_-\longrightarrow 0.\]
The semi-spin representations $S_\pm$ carry volume forms induced by scalar spinorial pairings. Moreover, $W$ has a canonical volume form since it is the semi-spin representation of $\Spin(6, \CC)\cong \SL(4, \CC)$. Comparing these volume forms under the above exact sequence gives an invariant $s\in\CC^\times$ of a rank $(2, 2)$ square-zero supercharge. Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parametrized by this invariant.

Let $N_\RR=\RR^4$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. We consider the 8-dimensional Euclidean vector space $N$ which carries a complex half-density. By the results of Section \ref{sect:8dtopologicaltwist} we obtain a family $Q_t$ of 8d square-zero supercharges. Its dimensional reduction to 4 dimensions also gives a family of 4d square-zero supercharges. Then from Theorem \ref{thm:8dHodgereduction} we obtain the following statement.

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the topological Hodge theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$.
\label{thm:4d422Hodgetwist}
\end{theorem}

Let us now rewrite the family $Q_t$ in 4-dimensional terms. Consider the Kapustin--Witten twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\subset \Spin(4, \RR)\times \Spin(2, \RR)\subset \Spin(6, \CC)$ under which $W$ decomposes as
\[W\cong S_+\oplus S_-.\]
In this case the spinorial representation becomes
\[\Sigma\cong S_+\otimes S_+\oplus S_+\otimes S_-\oplus S_-\otimes S_+\oplus S_-\otimes S_-.\]
In particular, there are two scalar supercharges $Q_+$ and $Q_-$ given by the volume forms on $S_+$ and $S_-$ respectively. We may then consider a family of supercharges
\[Q = u Q_+ + i v Q_-\]
for $u, v\in\CC$. If $u,v\neq 0$ we obtain a rank $(2, 2)$ supercharge. In this case the map $Q\colon S_+^*\cong S_+\rightarrow W$ is given by multiplication by $u$ and the map $Q\colon W\rightarrow S_-$ is given by multiplication by $iv$. Therefore, its $s$-invariant is
\[s = -\frac{u^2}{v^2}.\]

\begin{remark}
The family $uQ_+ + iv Q_-$ of square-zero supercharges is the same family as studied by Kapustin and Witten, see \cite[Section 3.1]{KapustinWitten}.
\end{remark}

These supercharges are related to $Q_t$ as follows. Let $S_+^8$ be the semi-spin representation of $\Spin(8, \CC)$ and $S_\pm$ the semi-spin representations of $\Spin(4, \CC)$ as before. Under the embedding
\[\Spin(4, \CC)\subset \Spin(4, CC)\times \Spin(4, \CC)\subset \Spin(8, \CC)\]
$S_+^8$ splits as
\[S_+^8\cong S_+\otimes S_+\oplus S_-\otimes S_-,\]
so $Q_+, Q_-\in S_+^8$. We then obtain
\[Q_0 = Q_+ + Q_-,\qquad \Bar{Q}_0 = Q_+ - Q_-.\]
Therefore, the $s$-invariant of the family $Q_t$ is
\begin{equation}
s = \frac{(1+t)^2}{(1-t)^2}.
\label{eq:4d4sinvariant}
\end{equation}

\begin{cor}
The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s=1$ is perturbatively equivalent to the topological BF theory $T^*[-1]\map(\RR^4_{\mathrm{dR}}, B\fg)$.
\end{cor}
\begin{proof}
The supercharge $Q_0$ has $s$-invariant $s=1$. By Theorem \ref{thm:4d422Hodgetwist} the twist by $Q_0$ is perturbatively equivalent to the specialization of the theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$ at $t=0$. By Proposition \ref{prop:Hodgetheoryspecialization} the latter is isomorphic to the topological BF theory $T^*[-1]\map(\RR^4_{\mathrm{dR}}, B\fg)$.
\end{proof}

\begin{cor}
The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s\neq 1$ is perturbatively trivial.
\end{cor}
\begin{proof}
For any $s\neq 1$ we may find $t\neq 0$ solving \eqref{eq:4d4sinvariant}. But by Proposition \ref{prop:Hodgetheoryspecialization} the specialization of the topological Hodge theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$ at $t\neq 0$ is perturbatively trivial.
\end{proof}
